\texttt{vqtl}: An \texttt{R} package for Mean-Variance QTL Mapping

### 2018-02-16 Package_vqt_Manuscript.tex
add zenodo DOI

\section*{Resources}
The scripts used to create the data and plots published here are available at \url{ZENODO}.
The software and its documentation are freely available on \texttt{CRAN} at \url{https://CRAN.R-project.org/package=vqtl}.

>>>>

\section*{Resources}
The scripts used to create the data and plots published here are available as a public, static Zenodo repository at \url{DOI: 10.5281/zenodo.1173799}.
The package \texttt{vqtl} and its documentation are freely available on \texttt{CRAN} at \url{https://CRAN.R-project.org/package=vqtl}.
